---
title: "Plot 3"
description: |
  Here I will briefly show the process I went through before getting the final version of the third plot, together with its final version.
author:
  - name: Tamara Niella
    url: https://www.linkedin.com/in/tniella/
date: 03-20-2019
output:
  radix::radix_article:
    self_contained: false
---


```{r setup, include=FALSE}

library(aod)
#install.packages("aod")
library(ggplot2)
library(here)
library(tidyverse)
library(rio)
library(magrittr)
library(skimr)
library(janitor)
library(fastDummies)
#install.packages("fastDummies")
library(reshape2)
library(wesanderson)
library(ggridges)
library(sundry)
library(colorblindr) 

knitr::opts_chunk$set(echo = FALSE)
```

```{r data wrangling}

#Load data 

dat_int<- import(here("sim_data_int.csv"))

#making variable names nice 

colnames(dat_int)[1]<- "mindset"

dat_int %<>% janitor::clean_names()

#getting rid of subjects that in the expeirment had some kind of problem (did't complete task well etc), and I am only keeping data from one participant per dyad, since initially, I will only look at answers that dyads answered together (same answer for both participants, I only need one)

dat_dyad<- dat_int %>% 
  filter(problem == 0, dyad_part == "A") 

#getting demographic data (for potential methods section)

dat_dem<- dat_int %>% 
  filter(problem == 0, gender > 0) %>%
  drop_na(age) %>%
  select(gender, age)

mean_age <- mean(dat_dem$age)
sd_age <- sd(dat_dem$age)
sum_fem <- dat_dem %>% 
  filter(gender == 2 )%>%
  summarize(fem = length(gender))

sum_dem <- dat_dem %>% 
  group_by(gender) %>%
  summarize(gen = length(gender))

#renaming variable value names, changing "treatment for doubt", to improve explanation of study through graphs and analysis

dat_dyad$mindset <-  gsub("Treatment", "Doubt", dat_dyad$mindset)

#coding mindset as factor 

dat_dyad$mindset <- as.factor(dat_dyad$mindset)

#stuff from plot 1 

#I want to see the dyad aswers for agreement (yes or no) for both stories, then I will create a new data set with one variable for agreement, that will iclude agreement for stories one and 2 and another variable that will indicate whether that agreement belongs to story 1 (freedom of speech) or 2 (cyber privacy)

mindset2 <- rep(dat_dyad$mindset, 2)
agreement <- c(dat_dyad$dyad_ag_s1, dat_dyad$dyad_ag_s2)
story <- as.factor(c(rep.int(1,36), rep.int(2,36)))


data<- data.frame(mindset2, agreement, story)

#change values of variable "story", names for numbers (I will only need this if I decide to show the proportions of agreement for the different stories - which is not totally relevant to the results of the study, so I am still debating about it )

data$story <- gsub("1", "Freedom of Speech", data$story)
data$story <- gsub("2", "Cyber Privacy", data$story)


```


# Plot 3's Goal

I want to compare the distribution of Judgement in the studied sample from Part 1 to Part 3 between the 2 different mindset groups. 

The goal is to communicate the effect of the mindset participants are given, in how much their opinion on a moral or political issue changes after discussing it with someone else. 

## First Version 

Density plots, divided by Mindset and the densities for each part stacked. 
Is a good start but the effect is not so clear. 

```{r try1p3}

#I am going to focus on data from the interaction condition and for this I will look at individual data (Parts 1 and 3 were done individually, not in pairs)

data_ok <- dat_int %>% filter(problem==0)
data_ok$mindset <-  gsub("Treatment", "Doubt", data_ok$mindset)

mindset3 <- rep(data_ok$mindset, 4)

judge_p1 <- c(data_ok$s1_judge_p1, data_ok$s2_judge_p1)
judge_p3 <- c(data_ok$s1_judge_p3, data_ok$s2_judge_p3)
judge <- c(judge_p1, judge_p3)
story3 <- rep(as.factor(c(rep.int(1,92), rep.int(2,92))),2)
part <-as.factor(c(rep.int(1,184), rep.int(3,184)))


data_3<- data.frame(mindset3, judge, story3,part)

data_3$story3 <- gsub("1", "Freedom of Speech", data_3$story3)
data_3$story3 <- gsub("2", "Cyber Privacy", data_3$story3)

data_3 %<>% drop_na(judge)


#New data wrangling based on JP suggestions: 

tn_dat <- dat_int %>% 
  filter(problem == 0) %>% 
  select(mindset, 
         s1_judge_p1,
         s2_judge_p1,
         s1_judge_p3,
         s2_judge_p3) %>% 
  gather(judge, score, -1) %>% 
  separate(judge, c("s_type", "delete", "part"), sep = "_") %>% 
  select(-delete)%>%
  drop_na(score)%>%
  rename(Mindset = mindset)

tn_dat$part <- gsub("p1", "Part 1", tn_dat$part)
tn_dat$part <- gsub("p3", "Part 3", tn_dat$part)

tn_dat$Mindset <- gsub("Treatment", "Doubt", tn_dat$Mindset)


ggplot(tn_dat, aes(score, color = part, fill = part))+
  geom_density(alpha = 0.5)+
  facet_wrap(~Mindset) +
  theme_minimal()

```

## Second Version 

Went for a density - ridges plot, that way the difference of distribution in part1 and 3 is clearer 



```{r try2p3}
#adding colors 
ggplot(tn_dat, aes(score,part))+
  geom_density_ridges(aes(fill=part))+
  facet_wrap(~Mindset) +
  theme_minimal() 


```

# Final Version

Decided to change the organization of the density ridges plot: decided to put Mindset on the y axis and facet wrap the plot on Part 1 and 3 , this way is easier to compare the change in distribution from part 1 to 3 between Control land Doubt mindsets. 

I also added important final details like title, subtitle, legends and color blind friendly color palette. 

```{r finalp3}


#Possible Final version: 

ggplot(tn_dat, aes(score,Mindset))+
  geom_density_ridges(aes(fill=Mindset, color= Mindset), alpha=.7)+
  scale_fill_OkabeIto(order=c(3,6))+
  scale_color_OkabeIto(order=c(3,6))+
  facet_wrap(~part) +
  labs(title = "Judgment Distribution", subtitle= "Judgment before (Part 1) and after (Part 3) discussion", x = "Judgment", y = "Density")+
  theme_minimal(base_size = 15)




```

## Interpretation 

The distribution of the Judgment on the moral/political issues is pretty similar in Part 1 for both Doubt and Control mindset groups. However, in Part 3 the distribution of judgment seems to have higher variability for the Doubt Mindset group, and seems to be almost bi-modal, while the distribution of judgment for the Control Mindset group is uni-modal and the variability seems to decrease. 

In a way, this supports our Hypothesis 3: Since, during the discussion part, there was a higher percentage of agreement in the control group, and therefore we now see a more Uni-modal distribution of judgment after the discussion (People's opinions get closer)