---
title: "Plot 2"
description: |
  Here I will briefly show the process I went through before getting the final version of the second plot, together with its final version.
author:
  - name: Tamara Niella
    url: https://www.linkedin.com/in/tniella/
date: 03-20-2019
output:
  radix::radix_article:
    self_contained: false
---

```{r setup, include=FALSE}

library(aod)
#install.packages("aod")
library(ggplot2)
library(here)
library(tidyverse)
library(rio)
library(magrittr)
library(skimr)
library(janitor)
library(fastDummies)
#install.packages("fastDummies")
library(reshape2)
library(wesanderson)
library(ggridges)
library(sundry)
library(colorblindr) 

knitr::opts_chunk$set(echo = FALSE)
```

```{r data wrangling}

#Load data 

dat_int<- import(here("sim_data_int.csv"))

#making variable names nice 

colnames(dat_int)[1]<- "mindset"

dat_int %<>% janitor::clean_names()

#getting rid of subjects that in the expeirment had some kind of problem (did't complete task well etc), and I am only keeping data from one participant per dyad, since initially, I will only look at answers that dyads answered together (same answer for both participants, I only need one)

dat_dyad<- dat_int %>% 
  filter(problem == 0, dyad_part == "A") 

#getting demographic data (for potential methods section)

dat_dem<- dat_int %>% 
  filter(problem == 0, gender > 0) %>%
  drop_na(age) %>%
  select(gender, age)

mean_age <- mean(dat_dem$age)
sd_age <- sd(dat_dem$age)
sum_fem <- dat_dem %>% 
  filter(gender == 2 )%>%
  summarize(fem = length(gender))

sum_dem <- dat_dem %>% 
  group_by(gender) %>%
  summarize(gen = length(gender))

#renaming variable value names, changing "treatment for doubt", to improve explanation of study through graphs and analysis

dat_dyad$mindset <-  gsub("Treatment", "Doubt", dat_dyad$mindset)

#coding mindset as factor 

dat_dyad$mindset <- as.factor(dat_dyad$mindset)
```

# Plot 2's goal: 

A bar graph comparing the proportion of agreement (y-axis) between the interaction condition (interaction agreement) and the imagine condition (imagine agreement) (x- axis, 1 bar per group).

The goal would be to communicate whether participant’s expectancy of agreement is different to the actual proportion of agreement when participants have a real interaction face-to-face.

## First version 

Proportion in the y-axis , some legends are too small

```{r try1p2}


#from plot 1 

#I want to see the dyad aswers for agreement (yes or no) for both stories, then I will create a new data set with one variable for agreement, that will iclude agreement for stories one and 2 and another variable that will indicate whether that agreement belongs to story 1 (freedom of speech) or 2 (cyber privacy)

mindset2 <- rep(dat_dyad$mindset, 2)
agreement <- c(dat_dyad$dyad_ag_s1, dat_dyad$dyad_ag_s2)
story <- as.factor(c(rep.int(1,36), rep.int(2,36)))


data<- data.frame(mindset2, agreement, story)

#change values of variable "story", names for numbers (I will only need this if I decide to show the proportions of agreement for the different stories - which is not totally relevant to the results of the study, so I am still debating about it )

data$story <- gsub("1", "Freedom of Speech", data$story)
data$story <- gsub("2", "Cyber Privacy", data$story)

#data set up

imagine <- import(here("sim_data_im.csv"))
data_im <- data.frame(imagine$s1_agrement_y_n, imagine$s2_agrement_y_n)

colnames(data_im)<- c("agreement_1im", "agreement_2im")

agreement_im <- c(data_im$agreement_1im, data_im$agreement_2im)
stories_im <- c(rep("Freedom of Speech", 34), rep("Cyber Privacy", 34) )
data_im_long <- data.frame(agreement_im, stories_im)

agreement_all <- c(agreement, agreement_im)
condition <- as.factor(c(rep.int("Interaction",72), rep.int("Imagine",68)))
stories_all <- as.factor(c(data$story, stories_im))

data_in_im <- data.frame(agreement_all, condition, stories_all)

#summary of proportions of agreement in imagine and interaction for plot 2 

summary_cond<- data_in_im%>% 
  group_by(condition)%>%
  summarize(prop_agreement =mean(agreement_all))

#JP Suggestion: 

summary_cond_s<- data_in_im%>% 
  group_by(condition, stories_all)%>%
  summarize(prop_agreement =mean(agreement_all),
            se_agree = sundry::se(agreement_all))

summary_cond_se1<- data_in_im%>% 
  group_by(condition)%>%
  summarize(prop_agreement =mean(agreement_all),
            se_agree = sundry::se(agreement_all))

summary_cond_se2<- data_in_im%>% 
  group_by(condition)%>%
  summarize(per_agreement =mean(agreement_all)*100,
            se_agree = sundry::se(agreement_all)*100)

#plot 2 - version without dividing by stories #NEW OK VERSION with error bars 

ggplot(summary_cond_se1, aes(condition, prop_agreement))+
  geom_col(alpha=.7, fill = c("#F1BB7B", "#FD6467"),width = .5)+
  geom_errorbar(aes(ymin = prop_agreement + qnorm(0.025)*se_agree,
                    ymax = prop_agreement + qnorm(0.975)*se_agree,
                    group = condition), size=.3, width= .2) +
  labs(title= "Agreement in Interaction  vs Expected Agreement in Imagine", x = "Condition", y = "Proportion of agreement")+
  theme_minimal()+
  ylim(0, 1)
```


## Second Version 

Increased font size for legends , changed proportion in the y-axis for percentage, for easier interpretation. 

```{r try2p2}


#NEW OK version of the plot above, with percentages, but with percentages signs: 


ggplot(summary_cond_se1, aes(condition, prop_agreement))+
  geom_col(alpha=.7, fill = c("#F1BB7B", "#FD6467"),width = .5)+
  geom_errorbar(aes(ymin = prop_agreement + qnorm(0.025)*se_agree,
                    ymax = prop_agreement + qnorm(0.975)*se_agree,
                    group = condition), size=.3, width= .15) +
  labs(title= "Imagined Agreement vs Interaction Agreement", x = "Condition", y = "Percentage of agreement")+
  theme_minimal(base_size = 15)+
  ylim(0, 1)+
  scale_y_continuous(labels = scales::percent)

```


# Final version: 

Changed colors for more color blind friendly ones. 

```{r finalp2}

#UPDATED VERSION - more color blind friendly colors #Darjeeling2 color palette

ggplot(summary_cond_se1, aes(condition, prop_agreement))+
  geom_col(alpha=.7, fill = c("#ECCBAE", "#046C9A"),width = .5)+
  geom_errorbar(aes(ymin = prop_agreement + qnorm(0.025)*se_agree,
                    ymax = prop_agreement + qnorm(0.975)*se_agree,
                    group = condition), size=.3, width= .15) +
  labs(title= "Imagined Agreement vs Interaction Agreement", x = "Condition", y = "Percentage of agreement")+
  theme_minimal(base_size = 15)+
  ylim(0, 1)+
  scale_y_continuous(labels = scales::percent)



```

## Interpretation: 

As we can see, out Hypothesis 2 is confirmed: people expect less agreement when they imagine having a discussion on a certain moral/political issue than the actual percentage of agreement when two people discuss that issue face to face. 
